---
title: "Pivoting Datasets"
subtitle: "STT2860 Intro to Data Management & Visualization S23"
author: "Author: YOUR NAME HERE"
date: "`r format(Sys.time(), '%A, %B %d, %Y @ %I:%M %p')`"
output: 
  html_document: 
    theme: cosmo
    highlight: textmate
---

```{r globaloptions, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```
***

### Packages Used

```{r packages}
library(tidyverse)
library(fivethirtyeight) # you will need to install this ONCE
```

### The `drinks` Dataset

Go to [Chapter 4 Data Importing and "Tidy" Data](https://moderndive.com/4-tidy.html) in *Modern Dive*.

#### Create `drinks_smaller`

```{r drinks_smaller}

```

#### Create `drinks_smaller_tidy`

```{r drinks_smaller_tidy_1}

```

```{r drinks_smaller_tidy_2}

```

```{r drinks_smaller_tidy_3}

```

Test with the `identical()` and `all.equal()` functions.

```{r identical_equal_test}

```

### The `dem_score` Dataset

#### Read in `dem_score`

```{r read_dem_score}
dem_score <- read_csv("../data_raw/dem_score.csv")
head(dem_score)
```

#### Create `guat_dem`

```{r guat_dem}

```

#### Create `guat_dem_tidy`

```{r guat_dem_tidy}

```

#### Create `dem_score_tidy`

```{r dem_score_tidy}

```

### The `bball` Dataset

#### Create `bball`

```{r bball}
bball <- tibble(
  player = rep(c("A", "B"), each = 4),
  year = rep(c(1, 1, 2, 2), times = 2),
  stat = rep(c("points", "assists"), times = 4),
  amount = c(14, 6, 18, 7, 22, 9, 38, 4)
)
bball
```

#### Create `bball_wide`

We want `points` and `assists` to be separate variables (columns).

```{r bball_wide}

```


***
```{r}
sessionInfo()
```
